Final Project Data 205

### 2021-12-08 Draft Final Project1.Rmd
Add files via upload

## Create a New Column and Add Months and years to WMATA DataSet 
```{r}
mutate(date=as.Date(date,format="%Y"))
```

@@

```{r}
#Create a time series 
```

@@

## Plot Types of Crime
```{r}
p2<-WMATA  %>%
  filter(type %in% c("ARREST","REPORT","SUMMONS/CITATION")) %>%
  ggplot(aes(x=type, fill= type))+
  geom_bar()+
  labs(title="Classification of Type of Crime/ Reporting",x="Type", y="Total")+
  scale_fill_brewer(palette = "Blues") + theme_minimal()
p2 + theme_minimal()
```

@@

# Create Plot on the Crimes Committed by State
```{r}

```
# Creat a Groupby type & count (tester)
```{r}
df_wmata %>%                         # Count rows by group
  group_by(type) %>% 
  summarize(n = n())
```

```{r}
df_type <-df_wmata
  group_by(type)
df_type
```

```{r}
df_type<- df_wmata %>%
 group_by(type) %>%
    summarize(count=n())

# Create Plot on Type of Crimes by Type
```{r}
ggplot(df_wmata, aes(x=type, fill=type )) + 
  geom_bar( ) +
  scale_fill_hue(c = 40) +
  theme(legend.position="none")
```

# Create Plot on 
```{r}

@@

## Remove Crimes Data 
```{r}
na.omit(crimes)
```

```{r}
view(crimes)
```

```{r}
names(crimes)[names(crimes) == 'Crime Name1'] <- 'Offenses'
```

```{r}
P1<-crimes %>%                        
  group_by(type) %>% 
  select("")
  summarize(n = n())
P1
```

```{r}
ggplot(crimes, aes(x=Offenses, fill=Offenses)) + 
  geom_bar( ) +
  scale_fill_hue(c = 40) +
  theme(legend.position="none")
```

>>>>

## Separate year from date
```{r}

@@

```{r}
#Create a time series plot
```

@@

## Plot Types of Crime
```{r}
p2<-WMATA  %>%
  filter(type %in% c("ARREST","REPORT","SUMMONS/CITATION")) %>%
  ggplot(aes(x=type, fill= type))+
  geom_bar()+
  labs(title="Classification of Type of Crime/ Reporting",x="Type", y="Total")+
  scale_fill_brewer(palette = "Blues") + theme_minimal()
p2 + theme_minimal()
```
## Facet_wrap on the types of reports throughout the years
```{r}
ggplot(data = WMATA,
       mapping = aes(x = date, y = n, color = type)) +
  geom_line() +
  facet_grid(rows = vars(type), cols =  vars(genus))
```

## Create a plot on
```{r}

@@

@@

## Create on plot on Income & Population(Linear Regression/ Scatterplot with Population)
```{r}

## Remove Crimes Data 
```{r}
Moco_crimes<-na.omit(crimes)
```

## Plot on Classifcation of Crime
```{r}
c1<-crimes  %>%
  filter(`Crime Name1` %in% c("Crime Against Person ","Crime Against Property","Crime Against Society")) %>%
  ggplot(aes(x=`Crime Name1`, fill=`Crime Name1`))+
  geom_bar()+
  labs(title="Classification of Crime",x="", y="Total")+
  scale_fill_brewer(palette = "Accent") + theme_minimal()
c1 + theme_minimal()
```

## 
```{r}
